Data Migration under a Changing Schema in Ampersand

### 2023-10-31 2022Migration/articleMigrationFACS.tex
fix some mistakes

      &\rules_\text{block}\cup(\rules_{\schema}\cap\rules_{\schema'}),\notag\\
      &\transactions_1\cup\transactions_2\cup\transactions_{\schema'},\notag\\

@@

   Assume that $\infsys$ and $\infsys'$ are information systems, so they satisfy definition~\ref{def:information system}.

@@

@@

      \text{isIS}\pair{\dataset_\infsys}{\schema_\infsys}\ \Rightarrow\ \text{isIS}\pair{\dataset_\infsys}{\schema_\migrsys}

@@

      \triple{a}{\overleftarrow{r}}{b}\in\triples_\infsys\ \Rightarrow\ \triple{a}{\overrightarrow{r}}{b}\in\triples_\migrsys

@@

      Note that
\item Prove that $\rels_2$ is redundant after the MoT,
      so the desired system can do without it.
      TBD
\item Prove that $\overleftarrow{\rels_{\schema}}$ is redundant after the MoT,
      so the desired system can do without it.
      TBD
\item 

@@

      \text{isIS}\pair{\dataset}{\schema_\migrsys}\ \Rightarrow\ \text{isIS}\pair{\dataset}{\schema'}

>>>>

      &\rules_\text{block}\cup\overrightarrow{\rules_{\schema}\cap\rules_{\schema'}},\notag\\
      &\transactions_1\cup\transactions_2\cup\overrightarrow{\transactions_{\schema'}},\notag\\

@@

   Assume that $\infsys=\pair{\dataset}{\schema}$ and $\infsys'=\pair{\dataset'}{\schema'}$ are information systems, so they satisfy definition~\ref{def:information system}.

@@

   We also assume that $\migrsys=\pair{\dataset_\migrsys}{\schema_\migrsys}$ is the migration system generated from $\infsys$ and $\infsys'$.

@@

      \text{isIS}\pair{\dataset}{\schema}\ \Rightarrow\ \text{isIS}\pair{\dataset}{\schema_\migrsys}

@@

      \triple{a}{r}{b}\in\triples_\infsys\ \Rightarrow\ \triple{a}{\overrightarrow{r}}{b}\in\triples_\migrsys

@@

@@

      \forall u\in\rules_{\schema'}-\rules_{\schema}.~\viol{\overrightarrow{u}}{\dataset}={\tt fixed}_u\ \Rightarrow\ (\text{isIS}\pair{\dataset}{\schema_\migrsys}\Leftrightarrow\text{isIS}\pair{\dataset}{\schema'})
